Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-19 papers/BON_VHDL/paper.tex
VHDL description

\documentclass{article} 
\usepackage{times}
\usepackage{multirow}
\usepackage{ifpdf}
\usepackage{a4wide}
\usepackage{pdfsync}

@@

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\Sc}{\emph{SYSTEM\_CHART}\xspace}
\newcommand{\Clc}{\emph{CLUSTER\_CHART}\xspace}
\newcommand{\Csc}{\emph{CLASS\_CHART}\xspace}
\newcommand{\Ft}{\emph{feature}\xspace}
\newcommand{\ent}{\emph{entity}\xspace}
\newcommand{\arch}{\emph{architecture}\xspace}
\newcommand{\archs}{\emph{architectures}\xspace}
\newcommand{\duc}{\emph{design units collection}\xspace}
\newcommand{\ducs}{\emph{design units collections}\xspace}
\newcommand{\du}{\emph{design unit}\xspace}
\newcommand{\undef}{\emph{undefined}\xspace}
%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

%======================================================================
\appendix
\section {APPENDIX}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\input{static}
%\todo{dragan 27/07/2009 - Figure out :  static types.}
\input{operators}
%\todo{dragan 27/07/2009 - Figure out :  types/subtypes.}
\input{types}
%======================================================================

>>>>

\documentclass{article} 
\usepackage{times}
\usepackage{multirow}
\usepackage{ifpdf}
\usepackage{a4wide}
\usepackage{pdfsync}
\usepackage{amsmath}
\usepackage{listings}

@@

\lstset{
  language=Java,
  basicstyle=\footnotesize\sffamily,
  identifierstyle=\itshape,
  stringstyle=\footnotesize\ttfamily,
  commentstyle=\textup,
  columns=flexible,
  captionpos=b,
  morekeywords={},
  literate=
  {-}{{$\textendash$}}1
  {<}{{$\textless$}}1
  {<=}{{$\textless=$}}1
  {>}{{$\textgreater$}}2
  {>=}{{$\textgreater=$}}2
  {\\}{{$\backslash\backslash$}}1
  {'}{{$\textprimstress$}}1
}

\def\lstinlinen{\lstinline[language=Bon,basicstyle=\normalsize\upshape]}

\def\lstinlinenv{\lstinline[language=VHDL,basicstyle=\normalsize\upshape]}

\def\lstinlinenc{\lstinline[language=VHDL,basicstyle=\normalsize\bfseries]}

\def\lstinlinenb{\lstinline[language=Bon,basicstyle=\normalsize\bfseries]}

\lstdefinelanguage{Bon} {
  morekeywords={require,ensure,feature,old,and,o,Q'slew,end,Result},
  morekeywords={class,delta,invariant,inherit,deferred,effective,NONE,make},
  morecomment=[l]{--}, 
  morecomment=[s]{/*}{*/}, 
  morestring=[b]", 
 literate=,
  showstringspaces=false
}

\lstdefinelanguage{VHDL} {
  morekeywords={not,xnor,and,nand, nor,or,xor,integer,byte,real},
  morekeywords={character,enum,type,boolean,bit,time,null,std_ulogic},
  morekeywords={sll, srl, sla, sra, rol, ror},
  morekeywords={rem,abs,mod},
  morekeywords={terminal,T'reference, T'contribution,T'tolerance},
  morekeywords={reference,contribution},
  morekeywords={nature,subnature,electrical,magnetic,translational,translational_v},
  morekeywords={rotational,rotational_v,fluidic,thermal,radiant},
  morekeywords={voltage,angular_velocity,pressure,velocity},
  morekeywords={current,force,torque,volumetric,flow_rate},
  morekeywords={T'left,T'right,T'high,T'ascending,T'image(x),T'value(s)},
  morekeywords={left,right,high,ascending,image,value},
  morekeywords={T'pos(s),T'val(x),T'succ(x),T'pred(x)},
  morekeywords={pos,val,succ,pred},
  morekeywords={A'left(n),A'right(n),A'low(n),A'high(n)},
  morekeywords={left,right,low,high},
  morekeywords={A'range(n),A'reverse_range(n),A'length(n),A'ascending(n)},
  morekeywords={range,reverse_range,length,ascending},
  morekeywords={T'leftof(x),T'rightof(x),T'base},
  morekeywords={leftof,rightof,base},
  morekeywords={Q'tolerance, Q'above,Q'delayed,Q'dot,Q'integ},
  morekeywords={delayed,dot,integ},
  morekeywords={Q'slew,Q'ztf,Q'ltf,Q'zoh},
  morekeywords={N'across, N'through},
  morekeywords={across,through,zoh,ltf,slew,ztf},
  morekeywords={above,tolerance,group,quantity},
  morecomment=[l]{--}, 
  morecomment=[s]{/*}{*/}, 
  morestring=[b]", 
 literate=,
  showstringspaces=false
}

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\ent}{\emph{entity}\xspace}
\newcommand{\arch}{\emph{architecture}\xspace}
\newcommand{\archs}{\emph{architectures}\xspace}

\newcommand{\undef}{\emph{undefined}\xspace}
\newcommand{\arcoss}{\emph{across}\xspace}
\newcommand{\through}{\emph{through}\xspace}
%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

%======================================================================
\appendix
\newpage
\section {APPENDIX}
\input{static}
\input{arith}
\input{shift}
\input{relation}
\input{logic}
\input{types}
\input{assignment}
\input{iscaltypeattr}
\input{tolerance}
\input{effort}
\input{flow}
\input{nature}
\input{iscalnature}
\input{iarrayattr}
\input{scalnat}
\input{iterminal}
\input{terminal}
\input{iquantity}
\input{quantity}
\input{quantityport}
\input{terminalport}
\input{signal}
\input{signalattr}
\input{wait}
%\input{quantityattr1}
%\input{quantityattr2}
%\input{quantityattr3}
%======================================================================

### 2009-08-19 papers/BON_VHDL/static.tex
added more types
VHDL description

\begin{center}
    \begin{tabular}{|l|l|l|}
    	\hline
    	VHDL-AMS & BON & Description \\ \hline
    	\ducs (packages) & \Sc & 
	\begin{minipage}[c]{7cm} 
                 \vskip 3mm
    		VHDL-AMS allows hierarchical structure modeling, 
    		meaning that subsistems (\ducs), can be developed independently.
    		As an top-level description (informal/formal), \Sc connect all the \ducs
    		together to a complete design. Actually \Sc can be understood 
                as VHDL-AMS package as a way of grouping a collection of related 
                declarations that serve a common purpose.
                \\ 
    	\end{minipage}\\ \hline
        \duc & \Clc &
	\begin{minipage}[c]{7cm} 
                \vskip 3mm
		An  subsistem which represent \duc.
                \\ 
    	\end{minipage}\\ \hline
	 \du & \Csc &
	\begin{minipage}[c]{7cm}
	      \vskip 3mm	 
              \Csc  describes \du. It can be identify with the primary unit (\ent) and secondary 
	      unit (\arch) structure in VHDL-AMS.
	      The \Csc's name corresponds to the name of the entity in VHDL-AMS.
              \\
    	\end{minipage}\\ \hline
        \arch & \Ft & 
	\begin{minipage}[c]{7cm} 
              \vskip 3mm
	      The feature section of the \Csc, where the mathematical 
	      transfer function of the component is entered, holds the same information 
	      as the \arch section of the VHDL-AMS.
              \\
    	\end{minipage}\\ \hline

>>>>

\newcommand{\duc}{\emph{design units collection}\xspace}
\newcommand{\ducs}{\emph{design units collections}\xspace}
\newcommand{\du}{\emph{design unit}\xspace}
\begin{center}
\begin{tabular}{ c  c  c }
\multicolumn{3}{c}{\textbf{STATIC TYPES}}\\ 
\hline \hline
VHDL-AMS & BON & Description \\ 
\hline \hline
% first element
\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\ducs
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|SYSTEM_CHART|  
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
         \smallskip \smallskip
	VHDL-AMS allows hierarchical structure modeling, 
	meaning that subsistems (\ducs), can be developed 
        independently. As an top-level description 
        (informal/formal), \lstinlinen|SYSTEM_CHART|
        connect all the \ducs together 
        to a complete design. Actually \lstinlinen|SYSTEM_CHART|
        can be understood as VHDL-AMS package as a way of grouping 
        a collection of related declarations that serve a common 
        purpose.
        \smallskip \smallskip
\end{minipage}\\

% next element

\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\duc
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|CLUSTER_CHART| 
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
      \smallskip \smallskip	 
      An  subsistem which represent \duc.
      \smallskip \smallskip
\end{minipage}\\

% next element

\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\du
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|CLASS_CHART| 
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
      \smallskip \smallskip	 
      \lstinlinen|CLASS_CHART|  describes \du. 
      It can be identify with the primary unit (\ent) 
      and secondary unit (\arch) structure in VHDL-AMS. 
      The \lstinlinen|CLASS_CHART|'s name corresponds 
      to the name of the entity in VHDL-AMS.
      \smallskip \smallskip
\end{minipage}\\

% next element

\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\arch
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|feature|
\smallskip \smallskip
\end{minipage}
&
\begin{minipage}[c]{6cm} 
      \smallskip \smallskip
      The feature section of the \lstinlinen|CLASS_CHART|, 
      where the mathematical transfer function of the component 
      is entered, holds the same information as the \arch section 
      of the VHDL-AMS.
      \smallskip \smallskip 
\end{minipage}\\
